A lottery model of density-dependent selection

### 2017-11-03 manuscript.tex
l

\begin{figure}
\centering
\includegraphics[scale=0.6]{Ksel.pdf}
\caption{\label{fig:Ksel} MacArthur's argument for why ``fitness is $K$'' in crowded environments (adapted from \citep[pp. 147]{macarthur_1967}). Arrows show the local direction of the dynamical trajectories of Eq.~\eqref{eq:macgeneral}. The nullclines where $f_1(n_1,n_2)=0$ and $f_2(n_1,n_2)=0$ need not be linear, but the ``carrying capacities'' $K$ are then less informative about the nullcline structure. Assuming these nullclines exist, exclusion is certain unless a type's nullcline extends out to greater densities in some region (here the outcome depends on initial condition).}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.8]{Kplot.pdf}
\caption{\label{fig:Ksel} (a) MacArthur's dynamical argument for why ``fitness is $K$'' in crowded environments. The nullclines where $f_1(n_1,n_2)=0$ and $f_2(n_1,n_2)=0$ need not be linear, but the ``carrying capacities'' $K$ are then less informative about the nullcline structure. Assuming these nullclines exist, exclusion is certain unless a type's nullcline extends out to greater densities in some region (here the outcome depends on initial condition).}
\end{figure}
